---
title: "Reproducible Research: Peer Assessment 1"
autor: "Roberth Araujo"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data<-read.csv("activity.csv", sep = ",", header = T)
str(data)
```
### Date format configuration
```{r}
library(lubridate)
data$date<-ymd(data$date)
str(data)
```
## What is mean total number of steps taken per day?
- Histogram of the total number of steps taken each day:
```{r}
data2<-with(data, tapply(steps, date, sum))
res<-data.frame(Date=ymd(names(data2)), Steps=data2)
hist(res$Steps, col="green", main = "Number of steps taken each day", xlab= "Steps")
```


- Mean and median total number of steps taken per day:
```{r, echo=TRUE}
meand<-mean(res$Steps, na.rm = TRUE)
meand
mediand<-median(res$Steps, na.rm = TRUE)
mediand
```

## What is the average daily activity pattern?
- Daily activity pattern
```{r}
data3<-aggregate(steps~interval, data, mean)
plot(data3$steps~data3$interval,type="l", col="green", main = "Average daily activity pattern", xlab= "Interval", ylab = "Number of steps")
```


- The interval with the maximum number of steps is:
```{r}
max<-data3[which.max(data3$steps),1]
max
```

## Imputing missing values

- Total number of missing values in the dataset:
```{r}
miss<-sum(is.na(data))
miss
```


- Strategy for filling in all of the missing values in the dataset:
```{r}
newarray <- numeric()
for (i in 1:nrow(data)) {
    rows <- data[i, ]
    if (is.na(rows$steps)) {
        steps <- subset(data3, interval == rows$interval)$steps
    } else {
        steps <- rows$steps
    }
    newarray <- c(newarray, steps)
}
```


- New dataset:
```{r}
data4<-data
data4$steps<-newarray
str(data4)
```


- Histogram of the total number of steps taken each day:

```{r}
data5<-with(data4, tapply(steps, date, sum))
res3<-data.frame(Date=ymd(names(data5)), Steps=data5)
hist(res3$Steps, col="green", main = "Number of steps taken each day", xlab= "Steps")
```


- Report the mean and median total number of steps taken per day:
```{r, echo=TRUE}
meand<-mean(res3$Steps, na.rm = TRUE)
meand
mediand<-median(res3$Steps, na.rm = TRUE)
mediand
```

## Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE}
data4$day <- weekdays(as.Date(data4$date))
```


- Weekdays dataset
```{r, echo=TRUE}
data6<-data4[(!data4$day %in% c("domingo","sábado")),]
head(data6)
```


- Weekends dataset
```{r, echo=TRUE}
data7<-data4[(data4$day %in% c("domingo","sábado")),]
head(data7)
```

- Plot
```{r, echo=TRUE}
par(mfrow=c(2,1), mar=c(5,4,2,1))
data8<-aggregate(steps~interval, data6, mean)
plot(data8$steps~data8$interval,type="l", col="red", main = "Average daily activity pattern in weekdays", xlab= "Interval", ylab = "Number of steps")
data9<-aggregate(steps~interval, data7, mean)
plot(data9$steps~data9$interval,type="l", col="black", main = "Average daily activity pattern in weekends", xlab= "Interval", ylab = "Number of steps")
```
