---
title: "Reproducible Research: Peer Assessment 1"
autor: "Roberth Araujo"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data<-read.csv("activity.csv", sep = ",", header = T)
str(data)
```
### Date format configuration
```{r}
library(lubridate)
data$date<-ymd(data$date)
str(data)
```
## What is mean total number of steps taken per day?
- Histogram of the total number of steps taken each day:
```{r}
data2<-with(data, tapply(steps, date, sum))
res<-data.frame(Date=ymd(names(data2)), Steps=data2)
hist(res$Steps, col="green", main = "Number of steps taken each day", xlab= "Steps")
```


- Mean and median total number of steps taken per day:
```{r, echo=TRUE}
meand<-mean(res$Steps, na.rm = TRUE)
meand
mediand<-median(res$Steps, na.rm = TRUE)
mediand
```

## What is the average daily activity pattern?
- Daily activity pattern
```{r}
data3<-aggregate(steps~interval, data, mean)
plot(data3$steps~data3$interval,type="l", col="green", main = "Average daily activity pattern", xlab= "Interval", ylab = "Number of steps")
```


- The interval with the maximum number of steps is:
```{r}
max<-data3[which.max(data3$steps),1]
max
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
